Dependent Object Types

### 2012-08-10 article.tex
ouch

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma \emptyset T, \forall k$. The
non-trivial case is to need to show ${t'} \in \relv {k-j-1} {\Gamma''}
{s'} T$ by supposing $k > 0$, $(\Gamma'; s) \in \rels k \Gamma \emptyset$, and, for some
$j < k$, $\reductionl {t} s {t'} {s'} j \andl \irred {t'}
{s'} \andl {\Gamma''} \in \relg \Gamma k {s'} {\Gamma'}$.

\todo{expand on why this non-trivial subcase is all that is needed for each case.}

@@

\begin{proofsketch}
Because $S$ is a subtype of $U$, it should hold that the expansion of
$S$ subsumes the expansion of $U$. Therefore, for $v \in \relv k
\Gamma s U$, we have fewer and ``simpler'' definitions to check than
for $v \in \relv k \Gamma s S$. One worry is potential narrowing
issues for methods: because the parameter type is contravariant, $U$
can require a more precise type than $S$. This should be fine, because
if the parameter type becomes ill-typed, then the check is vacuously
true.
\end{proofsketch}

\todo{possible pitfall with narrowing needs more cautiousness}

@@

\todo{explain that this is the reason why extending the store is so
  flexible}

\begin{proofsketch}
For the monotonicity with regards to the step-index, this follows
directly from the definitions of $\mathcal{E}$ and $\mathcal{V}$. For the
environment and the store, this follows from the definition of $\rels
k {\Gamma \envplus{x : S}} s$. To extend the environment and the store
for $x : S$, we can append as much as we want to $\Gamma$ and $s$, to
get $\Gamma'$ and $s'$, and then ignore the last element which is for
$x : S$.
\end{proofsketch}

>>>>

\begin{myproof}
The proof is on induction on the derivation of $\Gamma \ts t : T$. For
each case, we need to show $t \in \rele k \Gamma \emptyset T, \forall
k$. The non-trivial case is when $k > 0$ and for some $j < k$,
$\reductionl {t} s {t'} {s'} j \andl \irred {t'} {s'}$. Then, we need
to show ${t'} \in \relv {k-j-1} {\Gamma''} {s'} T$ for ${\Gamma''} \in
\relg \Gamma k {s'} {\Gamma'}$.

@@

\begin{proofsketch}
Because $S$ is a subtype of $U$, it should hold that the expansion of
$S$ subsumes the expansion of $U$. Therefore, for $v \in \relv k
\Gamma s U$, we have fewer definitions to check than for $v \in \relv
k \Gamma s S$.

There are two {\it potential pitfalls}.

First, because we don't check for type labels, we can end up in a
situation where a type label defined in both $S$ and $U$ is actually
only used meaningfully in $U$, and so $v \in \relv k \Gamma s S$ never
enforces it. Consider $v$ to map to $\Top \refine z {\ldecl l \Top}
\ldefs{l = v}$, $S$ is $\Top \refine z {\Ldecl L \Top \Top , \ldecl l
  \Top}$ and $U$ is $\Top \refine z {\Ldecl L \Top \Top , \ldecl l
  {z.\Top}}$. Now, $v \in \relv k \Gamma s S$ even though it doesn't
define the type label $L$. But $v \not\in \relv k \Gamma s U$ because
$v.L$ is not well-formed. \remark{Counterexample!}

Another worry is potential narrowing issues for methods: because the
parameter type is contravariant, $U$ can require a more precise type
than $S$. This should be fine, because if the parameter type becomes
non-expanding, then the check is vacuously true.
\end{proofsketch}

@@

\begin{proofsketch}
For the monotonicity with regards to the step index, this follows
directly from the definitions of $\mathcal{E}$ and $\mathcal{V}$. For
the environment and the store, this follows by design from the
definition of $\rels k {\Gamma \envplus{x : S}} s$. To extend the
environment and the store for $x : S$, we can append as much as we
want to $\Gamma$ and $s$, to get $\Gamma'$ and $s'$, and then ignore
the last element which is for $x : S$.
\end{proofsketch}
